Authentication based on DRAM PUFs

### 2024-06-26 latexPaper/paper.tex
push to github

\section{Implementation Objectives}
In order to analyze the various presented methods, measurements have to be made. Almost all surveyed papers use either hamming distance and fractional hamming distance or jaccard index for measuring the properties of the PUFs. The usage of one over the other is debatable although Xiong et al claims jaccard index to be a better metric because it takes into consideration only the bits that flip as opposed to fractional hamming distance which weighs all bits of the CRP equally.

@@

\[C_{1} = [n_{1}, k_{1}, d_{1}] \quad\text{and}\quad C_{2} = [n_{2}, k_{2}, d_{2}]\]

@@

@@

>>>>

\section{Implementation Objectives}
In order to analyze the various presented methods, measurements have to be made. Almost all surveyed papers use either hamming distance and fractional hamming distance or jaccard index for measuring the properties of the PUFs.\cite{jaccard} The usage of one over the other is debatable although Xiong et al claims jaccard index to be a better metric because it takes into consideration only the bits that flip as opposed to fractional hamming distance which weighs all bits of the CRP equally.

@@

\[C_{1} = [n_{1}, k_{1}, d_{1}]\] 
\[C_{2} = [n_{2}, k_{2}, d_{2}]\]

@@

    \bibitem{KELLER}
    C. Keller et al., "Dynamic memory-based physically unclonable function for the generation of unique identifiers and true random numbers," 2014 IEEE International Symposium on Circuits and Systems (ISCAS), 2014, pp. 2740-2743, doi: 10.1109/ISCAS.2014.6865740.

@@

    \bibitem{jaccard}
    Jaccard, P. (1901) étude Comparative de la distribuition florale dans une portion des Alpes et des Jura. Bulletin de la Société Vaudoise des Sciences Naturelles, 7, 547-579.
